\documentclass{article}
\usepackage[backend=biber,natbib=true,style=alphabetic,maxbibnames=50]{biblatex}
\addbibresource{/home/nqbh/reference/bib.bib}
\usepackage[utf8]{vietnam}
\usepackage{tocloft}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=red,citecolor=magenta]{hyperref}
\usepackage{amsmath,amssymb,amsthm,enumitem,float,graphicx,mathtools,tikz}
\usetikzlibrary{angles,calc,intersections,matrix,patterns,quotes,shadings}
\allowdisplaybreaks
\newtheorem{assumption}{Assumption}
\newtheorem{baitoan}{}
\newtheorem{cauhoi}{Câu hỏi}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{dangtoan}{Dạng toán}
\newtheorem{definition}{Definition}
\newtheorem{dinhly}{Định lý}
\newtheorem{dinhnghia}{Định nghĩa}
\newtheorem{example}{Example}
\newtheorem{ghichu}{Ghi chú}
\newtheorem{hequa}{Hệ quả}
\newtheorem{hypothesis}{Hypothesis}
\newtheorem{lemma}{Lemma}
\newtheorem{luuy}{Lưu ý}
\newtheorem{nhanxet}{Nhận xét}
\newtheorem{notation}{Notation}
\newtheorem{note}{Note}
\newtheorem{principle}{Principle}
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{question}{Question}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{vidu}{Ví dụ}
\usepackage[left=1cm,right=1cm,top=5mm,bottom=5mm,footskip=4mm]{geometry}
\def\labelitemii{$\circ$}
\DeclareRobustCommand{\divby}{%
	\mathrel{\vbox{\baselineskip.65ex\lineskiplimit0pt\hbox{.}\hbox{.}\hbox{.}}}%
}
\def\labelitemii{$\circ$}
\setlist[itemize]{leftmargin=*}
\setlist[enumerate]{leftmargin=*}

\title{Universities {\it\&} Research Institutes -- Trường Đại Học {\it\&} Viện Nghiên Cứu}
\author{Nguyễn Quản Bá Hồng\footnote{A Scientist {\it\&} Creative Artist Wannabe. E-mail: {\tt nguyenquanbahong@gmail.com}. Bến Tre City, Việt Nam.}}
\date{\today}

\begin{document}
\maketitle
\begin{abstract}
	This text is a part of the series {\it Some Topics in Elementary STEM \& Beyond}:
	
	{\sc url}: \url{https://nqbh.github.io/elementary_STEM}.
	
	Latest version:
	\begin{itemize}
		\item {\it Universities \& Research Institutes -- Trường Đại Học \& Viện Nghiên Cứu}.
		
		PDF: {\sc url}: \url{https://github.com/NQBH/elementary_STEM_beyond/blob/main/learning_teaching_research/university/NQBH_university.pdf}.
		
		\TeX: {\sc url}: \url{https://github.com/NQBH/elementary_STEM_beyond/blob/main/learning_teaching_research/university/NQBH_university.tex}.
	\end{itemize}
\end{abstract}
\tableofcontents

%------------------------------------------------------------------------------%

\section{Vietnam National University Ho Chi Minh City VNUHCM -- Đại Học Quốc Gia TP Hồ Chí Minh}

\subsection{Ho Chi Minh City University of Science HCMUS -- Trường Đại Học Khoa Học Tự Nhiên ĐHKHTN TP HCM}
\begin{enumerate}
	\item Website HCMUS: \url{https://hcmus.edu.vn/}.
	\item Website Faculty of Mathematics \& Computer Science: \url{https://www.math.hcmus.edu.vn/}.
\end{enumerate}

%------------------------------------------------------------------------------%

\subsection{Ho Chi Minh City University of Technology HCMUT -- Trường Đại Học Bách Khoa TP HCM}

%------------------------------------------------------------------------------%

\section{Ho Chi Minh University of Pedagogy HCMUE -- Trường Đại Học Sư Phạm TP HCM}

%------------------------------------------------------------------------------%

\section{Industrial University of Ho Chi Minh City IUH -- Trường Đại Học Công Nghiệp TP HCM}

%------------------------------------------------------------------------------%

\section{University of Management \& Technology UMT -- Trường Đại học Quản lý \& Công nghệ TP.HCM}
\begin{enumerate}
	\item Website UMT: \url{https://www.umt.edu.vn}.
	\item Facebook UMT official page: \href{https://www.facebook.com/UMTUniversity}{Facebook{\tt/}UMT -- Trường Đại học Quản lý \& Công nghệ TP.HCM}.
	\item Facebook UMT group: \href{https://www.facebook.com/groups/690300442040851}{Facebook{\tt/}Cộng Đồng Sinh Viên UMT}.
	\item {\bf Fee.} \href{https://giaoduc.net.vn/sv-hoc-tin-chi-truong-thu-tien-theo-ky-dh-quan-ly-va-cong-nghe-tphcm-noi-gi-post238408.gd}{SV học tín chỉ, trường thu tiền theo kỳ: ĐH Quản lý  \&  Công nghệ TP.HCM nói gì?}
\end{enumerate}
{\bf Slogan.} ``Với tinh thần giáo dục khai phóng, hệ sinh thái hợp tác quốc tế \& doanh nghiệp toàn diện, UMT hướng đến xây dựng một ngôi trường đại học thành công \& hạnh phúc, nơi mọi sinh viên đều được phát triển tiềm năng tối đa để tự do lựa chọn định hướng cho bản thân, linh động làm được nhiều ngành nghề trong môi trường đa văn hóa, sẵn sàng thích ứng với mọi biến động trong thế giới số 4.0, tự tin trở thành công dân toàn cầu, kiến tạo tương lai \& đóng góp cho cộng đồng.''

%------------------------------------------------------------------------------%

\section{Vietnam National University Ha Noi VNUHN -- Đại Học Quốc Gia Hà Nội}

\subsection{Ha Noi University of Science HNUS -- Trường Đại Học Khoa Học Tự Nhiên ĐHKHTN HN}

%------------------------------------------------------------------------------%

\section{Henri Lebesgue Centre de Math\'ematiques -- Trung Tâm Toán Học Henri Lebesgue}
\begin{enumerate}
	\item Official website: \url{https://www.lebesgue.fr/}.
\end{enumerate}

%------------------------------------------------------------------------------%

\section{Universit\'e en Rennes 1, France -- University of Rennes 1 -- Trường Đại Học Rennes 1, Pháp}
\begin{enumerate}
	\item Official Website: \url{https://www.univ-rennes.fr/}.
\end{enumerate}

\subsection{Wikipedia{\tt/}University of Rennes 1}
{\sf Motto.} {\it La volonté de progresser, d'innover, d'entreprendre} -- The will to progress, innovate, \& undertake. ``The {\it University of Rennes 1} was a \href{https://en.wikipedia.org/wiki/Public_university}{public university} located in \href{https://en.wikipedia.org/wiki/Rennes}{Rennes}, France. It was founded in 1970, after splitting of the historic \href{https://en.wikipedia.org/wiki/University_of_Rennes}{University of Rennes} into 2 universities. On Jan 1, 2023, the University of Rennes 1 merged with 5 \href{https://en.wikipedia.org/wiki/Grandes_%C3%A9coles}{grandes \'ecoles}: \href{https://en.wikipedia.org/wiki/EHESP}{Ecole des Hautes Etudes en Sant\'e Publique}, \href{https://en.wikipedia.org/wiki/%C3%89cole_nationale_sup%C3%A9rieure_de_chimie_de_Rennes}{\'Ecole nationale sup\'erieure de chimie de Rennes}, \href{https://en.wikipedia.org/wiki/ENS_Rennes}{ENS Rennes}, \href{https://en.wikipedia.org/wiki/INSA_Rennes}{INSA Rennes}, \& \href{https://en.wikipedia.org/wiki/Institut_d%27%C3%A9tudes_politiques_de_Rennes}{Sciences-Po Rennes} to create the new \href{https://en.wikipedia.org/wiki/University_of_Rennes}{University of Rennes}.

\subsubsection{History}

\begin{itemize}
	\item {\sf Creation of the University of Brittany.} Asked by \href{https://en.wikipedia.org/wiki/Francis_II,_Duke_of_Brittany}{Francis II, Duke of Brittany}, the Pope created the 1st university of Brittany in \href{https://en.wikipedia.org/wiki/Nantes}{Nantes} in 1460. It taught arts, medicine, law, \& theology. In 1728, the mayor of Nantes, G\'erard Mellier, asked that the university be moved to Rennes, which was more trade orientated already had the Parliament of Brittany. The law school was moved the Rennes in 1730. In 1793 the \href{https://en.wikipedia.org/wiki/French_Revolution}{French Revolution} closed all universities \& it was not before 1806 that the Law school reopened in Rennes.
	\item {\sf Development of the faculties in Rennes.} In 1808, \href{https://en.wikipedia.org/wiki/Napoleon_I_of_France}{Napoleon I} reorganized the universities in France, creating the \href{https://en.wikipedia.org/wiki/University_of_France}{University of France}. From the 2 original cities housing the University of Brittany, only Rennes was included in this University. Nantes had to wait until 1970 to have again its \href{https://en.wikipedia.org/wiki/University_of_Nantes}{University of Nantes}. In 1810 a faculty of letters opened, which gathered in 1839 5 schools (French literature, foreign literature, ancient literature, history, \& philosophy). The science faculty opened still in Rennes in 1840. Those 3 faculties remained without clear boundaries between them until 1885 with the creation of a ``Conseil des facult\'es'' which took in 1896 the name of University of Rennes. In the middle of the 19th century, they were gathered in the Palais Universitaire, located currently in the Quai \'Emile Zola, but were then scattered downtown. The faculty of law \& the faculty of letter were thus relocated in 1909 in the S\'eminaire, located currently in the Place Hoche.
	\item {\sf Creation of the University of Rennes 1.} In 1969, in order to enforce the growth of French universities, a law was passed, splitting the \href{https://en.wikipedia.org/wiki/University_of_Rennes}{University of Rennes} into 2 new entities. This new university took the name of `University of Rennes 1'.
	\item {\sf Creation of the new University of Rennes.} In 2023, the University of Rennes 1 merged with 5 Grandes écoles: Ecole des Hautes Etudes en Santé Publique, École nationale supérieure de chimie de Rennes, ENS Rennes, INSA Rennes \& Sciences-Po Rennes in the `UNIR' project, in order to create the new University of Rennes. The University of Rennes 2 with other research institutes (CNRS, INRAE, Inria, Inserm \& CHU de Rennes) are associated with the project. The 6 establishments will be grouped together in an `Experimental Public Establishment' (EPE), weighing nearly 7,000 staff \& teachers, including a thousand researchers, 156 research laboratories \& 60,000 of the 68,000 students in the Breton capital, including 7,000 international students.
\end{itemize}

\subsubsection{Location}
Most of the university's 1.64 $\rm km^2$ of grounds lie within the city boundary of Rennes, but it has other sites dotted around \href{https://en.wikipedia.org/wiki/Brittany}{Brittany}. The 3 main \href{https://en.wikipedia.org/wiki/Campus}{campuses} are in Beaulieu (in the east of Rennes), Villejean (in the north-west of Rennes) \& a central campus.

Situated in the north-east of the city, the Beaulieu campus is a large complex that was still in development in 1969. Beaulieu is the home of more than a dozen science buildings (for the Faculties of mathematics, physics, biology, \& other schools e.g. \href{https://en.wikipedia.org/wiki/Institut_national_des_sciences_appliqu%C3%A9es_de_Rennes}{INSA}) \& one of philosophy. The sports facilities \& the students' entertainment building are also located there.

In the north-west, the Villejean campus gathers \href{https://en.wikipedia.org/wiki/University_of_Rennes_2_-_Upper_Brittany}{Rennes 2}'s Faculties of Foreign Languages, Arts, Human Sciences \& Social Sciences. Rennes I University's Faculty of Medicine is located on the edge of this Villejean campus, nearby Brittany's largest hospital center, Pontchaillou.

The {\it city center} holds 2 separate buildings: the Faculty of Law \& Political Science, \& the Faculty of Economical Science, in front of which a cloister houses the 2 faculties' library.

There are other sites in \href{https://en.wikipedia.org/wiki/Lannion}{Lannion}, \href{https://en.wikipedia.org/wiki/Saint-Brieuc}{Saint-Malo}, \href{https://en.wikipedia.org/wiki/Foug%C3%A8res}{foug\`eres} \& \href{https://en.wikipedia.org/wiki/Dinard}{Dinard}; some research centers in \href{https://en.wikipedia.org/wiki/Monterfil}{Monterfil}, \href{https://en.wikipedia.org/wiki/Paimpont}{Paimpont} \& the isle of Bailleron; \& a museum owned by the university in \href{https://en.wikipedia.org/wiki/Penmarch}{Penmarch}.

\subsubsection{Affiliated institutions}

{\sf Institute of technology of Saint-Malo.} Institute of Technology of Saint-Malo (or IUT of Saint-Malo) is a French higher education institution founded in 1994 \& located in Saint-Malo. It is attached to the University of Rennes 1 \& trains students from BAC to BAC $+3$ level. The Saint-Malo University Institute of Technology delivers 2 types of degrees: the University Technology Diplomas \& Professional Licenses.

\subsubsection{People}

\begin{itemize}
	\item {\sf Alumni.}
	\item {\sf Faculty.}
\end{itemize}

\subsubsection{Points of interest}
\href{https://en.wikipedia.org/wiki/Jardin_botanique_de_l%27Universit%C3%A9_de_Rennes}{Jardin botanique de l`Universit\'e de Rennes}.'' -- \href{https://en.wikipedia.org/wiki/University_of_Rennes_1}{Wikipedia{\tt/}University of Rennes 1}

%------------------------------------------------------------------------------%

\section{Humboldt-Universität zu Berlin, Deutschland -- Humboldt University of Berlin, Germany -- Trường Đại Học Humboldt ở Berlin, Đức}
\begin{enumerate}
	\item Official Website: \url{https://www.hu-berlin.de/}.
\end{enumerate}



\section{Weierstraß-Institut für Angewandte Analysis und Stochastik, Deutschland -- Weierstrass Institute for Applied Analysis \& Stochastics, Germany -- Viện Weierstrass cho Giải Tích Ứng Dụng \& Ngẫu Nhiên}
\begin{enumerate}
	\item Official website: \url{https://www.wias-berlin.de/}
\end{enumerate}

%------------------------------------------------------------------------------%

\section{Miscellaneous}

%------------------------------------------------------------------------------%

\printbibliography[heading=bibintoc]
	
\end{document}